## SD v cDeg Optimisation
  
Getting back to routine analysis...
  
The table below shows how the NW, NE, SE Clanfield data for `r params$Rpt_Month` compared against the quality criteria used by UKMON and NEMETODE
  
As members of UKMON, we endeavour to get SD* (the Standard Deviation of angular velocity of the mid frame of an event) to less than 0.3. 
  
As members of NEMETODE, we try to optimise our data to get cDeg ( the least squares fit to the angle of the meteor track) to be less than 0.02).
  

```{r echo = FALSE, include = TRUE, message = FALSE, warning = FALSE}
library(dplyr)
library(knitr)
File_In <<- (paste("D:/Meteor Camera Management/Monthly Reports/",params$Rpt_Month," ",params$Rpt_Year,"/",params$Rpt_Year,params$Rpt_Mon_Num,"ALLNAData_Quality.csv",sep=""))

File_Out <<- data.frame()
File_Out <<- read.csv(File_In)
kable(File_Out[,1:3])
```  
    
Charting these results over time we can see a clear improvement :
  
```{r echo = FALSE, out.width='100%'}

library(knitr)
File_In <<- (paste("D:/Meteor Camera Management/Monthly Reports/",params$Rpt_Month," ",params$Rpt_Year,"/","Chart_SD_V_CDEG_ALL_ALL_ALL_ .jpg",sep=""))

knitr::include_graphics(File_In)
```
  
Plotting SD and cDeg against each other for all 2017 events we see the following spread .
  
```{r echo = FALSE, out.width='100%'}

library(knitr)
File_In <<- (paste("D:/Meteor Camera Management/Monthly Reports/",params$Rpt_Month," ",params$Rpt_Year,"/","Chart_Scatter_SD_CDEG_",params$Rpt_Year,"_YTD_ALL_ .jpg",sep=""))

knitr::include_graphics(File_In)
```
  
There are outriders but only a few - the vast majority of events were optimised to within the SD and cDeg limits.