---
title: "Clanfield Meteor Station Report 2017-08"
header-includes: \usepackage{graphicx}
graphics: yes
author: 'Compiled by: Steve Bosley'
date: 'For Reporting Period 1st : 31st December 2017'
output:
  html_document:
    theme: united
    toc: yes
    toc_depth: 2
  odt_document: default
  pdf_document:
    keep_tex: yes
    toc: yes
    toc_depth: 2
params:
  Data_Folder:
    label: "Source of Reporting Data"
    value: D:/Meteor Camera Management/Monthly Reports/
  UFO_Folder:
    label: "UFO Capture Top Level Library"
    value: D:/Meteor Watch/  
  Rpt_Year:
    label: "Reporting Year:"
    value: 2017
    input: select
    choices: [2014, 2015, 2016, 2017, 2018]
  Rpt_Month:
    label: "Reporting Month:"
    value: December
    input: select
    choices: [January, February, March, April, May, June, July, August, September, October, November, December]
  Rpt_Mon: 
    label: "Month Prefix:"
    value: Dec
    input: select
    choices: [Jan, Feb, Mar, Apr, May, Jun, Jul, Aug, Sep, Oct, Nov, Dec]
  Rpt_Mon_Num:
    label: "Month Number:"
    value: 12
    input: slider
    min: 01
    max: 12
    step: 1
  Rpt_Mon_Num_Plus_1:
    label: "Month Number plus 1:"
    value: 13
    input: slider
    min: 02
    max: 13
    step: 1
---


```{r setup, include=FALSE}
options(scipen = 99)
knitr::opts_chunk$set(echo = TRUE)
```
  
\pagebreak
  
# Change History
  
V0.1  Initial Draft
  
V1.0  Final version, for publication
  
\pagebreak
  
```{r run-summary, include=FALSE}
library(knitr)
out = NULL
out = c(out, knit_child('Include_Summary.Rmd'))

```
`r paste(out, collapse = '\n')`
  
```{r run-highlights, include=FALSE}
library(knitr)
out = NULL
out = c(out, knit_child('Include_Highlights.Rmd'))

```
`r paste(out, collapse = '\n')`

```{r run-top5, include=FALSE}
out = NULL
out = c(out, knit_child('Include_Top_5.Rmd'))

```
`r paste(out, collapse = '\n')`
  
All the showers mentioned in this report are those calculated by UFO Analyser using data from a single station (camera). When they are consolidated with data from other stations it is quite possible that the final determined shower will differ from that reported here.
  
NB. The full table of `r params$Rpt_Year` YTD meteor counts can be found in Appendix A, at the end of this document. 
  
\pagebreak
  
```{r run-fireball-list, include=FALSE}
out = NULL
out = c(out, knit_child('Include_Fireball_List.Rmd'))

```
`r paste(out, collapse = '\n')`

```{r run-fireball-images, include=FALSE}
out = NULL
  
for (i in 1:rowsprt) {
  out = c(out, knit_child('Include_Fireball_JPGs.Rmd'))
}
```
`r paste(out, collapse = '\n')`


\pagebreak
  
```{r run-data-sharing, include=FALSE}
out = NULL
out = c(out, knit_child('Include_Data_Sharing.Rmd'))
```
`r paste(out, collapse = '\n')`

```{r run-meteor-magnitudes, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_Meteor_Magnitudes.Rmd'))
```
`r paste(out, collapse = '\n')`

```{r run-maintenance, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_Maintenance.Rmd'))
```
`r paste(out, collapse = '\n')`
  
\pagebreak
  
```{r run-nw-camera-status, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_NW_Camera_Status.Rmd'))
```
`r paste(out, collapse = '\n')`
  
  
```{r run-nw-camera-notes, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_NW_Camera_Notes.Rmd'))
```
`r paste(out, collapse = '\n')`

\pagebreak
  
```{r run-ne-camera-status, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_NE_Camera_Status.Rmd'))
```
`r paste(out, collapse = '\n')`
  
  
```{r run-ne-camera-notes, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_NE_Camera_Notes.Rmd'))
```
`r paste(out, collapse = '\n')`
  
\pagebreak
  
```{r run-se-camera-status, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_SE_Camera_Status.Rmd'))
```
`r paste(out, collapse = '\n')`
  
```{r run-se-camera-notes, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_SE_Camera_Notes.Rmd'))
```
`r paste(out, collapse = '\n')`
  
\pagebreak
  
```{r run-all-camera-status-ytd, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_ALL_Cameras_YTD_Status.Rmd'))
```
`r paste(out, collapse = '\n')`
  
```{r run-all-camera-notes-ytd, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_ALL_Cameras_YTD_Notes.Rmd'))
```
`r paste(out, collapse = '\n')`

\pagebreak
  
```{r run-ufo-orbit, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_UFO_Orbit.Rmd'))
```
`r paste(out, collapse = '\n')`
  
```{r run-radar-matches, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_RADAR_Matches.Rmd'))
```
`r paste(out, collapse = '\n')`
  
\pagebreak
  
#News
 
```{r run-ukmon-news, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_UKMON_News.Rmd'))
```
`r paste(out, collapse = '\n')`
  
```{r run-nemetode-news, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_NEMETODE_News.Rmd'))
```
`r paste(out, collapse = '\n')`  
  
```{r run-hag-news, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_HAG_News.Rmd'))
```
`r paste(out, collapse = '\n')`
  
```{r run-imo-news, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_IMO_News.Rmd'))
```
`r paste(out, collapse = '\n')`
  
```{r run-meteornews, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_MeteorNews.Rmd'))
```
`r paste(out, collapse = '\n')`
  
\pagebreak
  
#2017 Perseids Analysis
  
```{r run-r-suite, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_RSuite.Rmd'))
```
`r paste(out, collapse = '\n')`
  
  
\pagebreak
  
```{r run-system-lifetime-behaviour, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_System_Lifetime_Behaviour.Rmd'))
```
`r paste(out, collapse = '\n')`
  

\pagebreak
  
# Data Quality
  
```{r run-analysis-automation, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_Analysis_Automation.Rmd'))
```
`r paste(out, collapse = '\n')`

\pagebreak
  
  
```{r run-sd-v-cdeg, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_SD_v_cDeg.Rmd'))
```
`r paste(out, collapse = '\n')`
  
\pagebreak
  
```{r run-magnitude, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_Magnitude.Rmd'))
```
`r paste(out, collapse = '\n')`
  
\pagebreak
  
```{r app-a-shower-counts, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_App_A_Shower_Counts.Rmd'))
```
`r paste(out, collapse = '\n')`
  
\pagebreak
  
# Appendix B: Video Captures, by Category.
  
\normalsize

The following charts show the total counts for each of the defined event categories captured by the Clanfield cameras, with the data for 2014-16 for comparison. By monitoring changes in these counts, it is possible to highlight out of line situations - some of which need to be resolved (eg. electrical interference, spider incursions etc.) and others which can only be tolerated (eg. bat and bird fly bys) but, fortunately tend to be seasonal. 
  
NB. Keep an eye on the scale of the Y-axis to see how significant the events captured in each chart are.
  
NB. Starting in the new year I will drop the first two years from this chart to aid reading the x axis labels !  
  
```{r run-count-of-meteors2, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_Count_of_Meteors.Rmd'))
```
`r paste(out, collapse = '\n')`
  
```{r run-count-of-aircraft, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_Count_of_Aircraft.Rmd'))
```
`r paste(out, collapse = '\n')`  

```{r run-count-of-bats, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_Count_of_Bats.Rmd'))
```
`r paste(out, collapse = '\n')`
  
```{r run-count-of-birds, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_Count_of_Birds.Rmd'))
```
`r paste(out, collapse = '\n')`
  
```{r run-count-of-flashes, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_Count_of_Flashes.Rmd'))
```
`r paste(out, collapse = '\n')`
  
```{r run-count-of-insects, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_Count_of_Insects.Rmd'))
```
`r paste(out, collapse = '\n')`
  
```{r run-count-of-moon-effects, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_Count_of_Moon_Effects.Rmd'))
```
`r paste(out, collapse = '\n')`
  
```{r run-count-of-noise, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_Count_of_Noise.Rmd'))
```
`r paste(out, collapse = '\n')`
  
```{r run-count-of-spiders, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_Count_of_Spiders.Rmd'))
```
`r paste(out, collapse = '\n')`
  
```{r run-count-of-twilight, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_Count_of_Twilight.Rmd'))
```
`r paste(out, collapse = '\n')`
  
```{r run-count-of-weather, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_Count_of_Weather.Rmd'))
```
`r paste(out, collapse = '\n')`
  
```{r run-count-of-white-noise, include=FALSE}
out = NULL
  
out = c(out, knit_child('Include_Count_of_White_Noise.Rmd'))
```
`r paste(out, collapse = '\n')`  
  
  
  
# End of Report        
  